Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-02 trunk/lids/twittersearchwrap/paper/paper.tex
added a few remarks

@@

A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
%uhe: System beschreiben

@@

\begin{enumerate}
	\item In a first step, the most recent search results for the query are obtained. In our example, calling the Wrapper with query $\#ka$ will return a
document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.

An example for a single retrieved post is the following: \texttt{''Just returned from a wonderful holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets''}
\myremark{Frage}{Sollte man da auch noch die Metadaten (Autor, Uhrzeit) mit angeben?}

  \item In a second (optional) step hyperlinks posted in messages of the fetched feed are followed, content of the referenced website's body is fetched and processed by the Wrapper. The idea is to acquire additional content which is used as additional signal when searching for entities. We have thought of other methods for enriching the result, like searching for other messages posted by users which have posted messages in the result set. However, these alternative method are more likely to introduce noise in the signal which is used for obtaining relevant entities.

In our example, the message contains a link to\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the text found at the link gives us the following text:''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''

@@

	Continuing our example, the output RDF document contains the following triples to reference the DBPedia mappings: 
	\myremark{Uta}{Bei den Tripeln fehlt das Subjekt}
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
	Karlsruhe\_Institute\_of\_Technology"/>}

	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:

@@

The optional step of dereferencing URLs which are posted in messages contained in the result set can be triggered using the option \texttt{extern=true}. To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first $k$ words.
\myremark{TODO}{Was ist der cut-off-Wert?}

@@

\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
\section{Conclusion}
\label{sect:conclusion}

>>>>

The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
The corpus contains evaluation results solicited via Mechanical Turk.
In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
@@@even with hashtags we have ambiguity, how would be map Twitter message containing the keyword ``apple''?

Softic et al \cite{key:softic} have developed a framework and system for mining
data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
As such, our approach is closely related.
Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
% from stakovic et al.
%In order to make tweets more searchable and make them useful for the described
%scenario one would need to have represent them in a structured format and associate
%those tweets with the topics that refer to. As a basic approach we process the text of
%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
%concepts related to a tweet, but is useful only on a limited number of tweets directly
%mentioning a particular topic. In the example data set we produced from ESWC2010,
%tweet topics are represented using dc:subject property.

Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
The system we use for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.
%uhe: System beschreiben
Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
We too use external data to augment the set of Twitter messages supplied to the Wikifier system.

@@

@@

\begin{enumerate}
	\item In a first step, the most recent search results for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#ka$ will
	return a document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.

An example for a single retrieved post is the following: ''\texttt{Just
returned from a wonderful holiday in \#ka.
\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}'', posted by
Twitter user \texttt{sample\_user\_12345}; geo coordinates and the date
the message has been posted be furthermore known.

  \item In a second (optional) step hyperlinks posted in messages of the fetched
  feed are followed, content of the referenced website is fetched and processed by the Wrapper. The idea is to acquire additional content which is used as additional signal when searching for entities. We have thought of other methods for enriching the result, like searching for other messages posted by users which have posted messages in the result set. However, these alternative methods are more likely to introduce noise in the signal which is used for obtaining relevant entities.

In our example, the message contains a link to
\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
text found at the link gives us the following text: ''\texttt{Karlsruhe, where
paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''

@@

	Continuing our example, the output RDF document contains the following triples
	to reference the DBPedia mappings:\newline
	\texttt{<rdf:Description rdf:about=""/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
	Karlsruhe\_Institute\_of\_Technology"/>}\newline
	\texttt{</rdf:Description>}\newline
	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:

@@

The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true}. To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first 50 words.

@@

\subsection{Results}

\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}

\subsection{Discussion}

@@@highlight the remarkable outcomes
@@@what is did we learn from the results?

\section{Conclusion}
\label{sect:conclusion}
